Positive Correlation Between Racialization, Gendering and Police Strip Searches in the Toronto Municipal, 2020-2021

### 2024-01-26 outputs/paper/paper.qmd
fine-tune writing and finalize paper

Regarding @fig-reasons-race, due to the sheer number of police searches that people who are racially black and white have compared to other groups, this paper subsections the dataset on racialized police searches into two graphs. Both of these graphs are devoid of data from people are racially unknown or don't identify with any races--"None" or "Unknown or Legacy"--to ensure graph visibility. In specifics, graph (a) of @fig-reasons-race contains only the distribution from people who racially identify as black and white, while graph (b) of @fig-reasons-race contains the distribution of all other minority groups--except for black people--along with white people. This ensures data clarity between groups with higher counts of strip searches and groups with lower counts of strip searches. In addition, to ensure that data is proportionate to one another, the percentages for each racial group when subdivided into each of the different sums of reasons are calculated and used instead of `count`.

>>>>

Regarding @fig-reasons-race, count-wise, since people who are racially black and white have more strip searches compared to other groups, this paper subsections the dataset on racialized police searches into two graphs. Both of these graphs are devoid of data from people are racially unknown or don't identify with any races--"None" or "Unknown or Legacy"--to ensure graph visibility. In specifics, graph (a) of @fig-reasons-race contains only the distribution from people who racially identify as black and white, while graph (b) of @fig-reasons-race contains the distribution of all other minority groups--except for black people--along with white people. This ensures data clarity between groups with higher counts of strip searches and groups with lower counts of strip searches. In addition, to ensure that data is proportionate to one another, the percentages for each racial group when subdivided into each of the different sums of reasons are calculated and used instead of `count`.
